An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-11-04 EconGrowth2.Rnw
Resample scatter plots for all CES nestings now included.

@@

**** Include other nestings here? ****

>>>>

**** Include other nestings here ****

Coefficients for each resampled CES model (with energy)
are shown in 
Figures~\ref{fig:CESq_lambda_gamma_Scatter_Graph_kle}--\ref{fig:CESq_sigma_delta_Scatter_Graph_ekl}. 
Note that each nesting of the factors of production
is included in the graphs.

<<CESq_lambda_gamma_Scatter_Graph_kle, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $q$, ($kl$)$e$ nesting) resample model parameters $\\lambda$ and $\\gamma$.">>=
cesResamplePlotLambdaGamma(energyType="Q", nest="(kl)e")
@

<<CESq_sigma_1_delta_1_Scatter_Graph_kle, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $q$, ($kl$)$e$ nesting) resample model parameters $\\sigma_1$ and $\\delta_1$.">>=
cesResamplePlotSigma_1Delta_1(energyType="Q", nest="(kl)e")
@

<<CESq_sigma_delta_Scatter_Graph_kle, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $q$, ($kl$)$e$ nesting) resample model parameters $\\sigma$ and $\\delta$.">>=
cesResamplePlotSigmaDelta(energyType="Q", nest="(kl)e")
@

<<CESq_lambda_gamma_Scatter_Graph_lek, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $q$, ($le$)$k$ nesting) resample model parameters $\\lambda$ and $\\gamma$.">>=
cesResamplePlotLambdaGamma(energyType="Q", nest="(le)k")
@

<<CESq_sigma_1_delta_1_Scatter_Graph_lek, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $q$, ($le$)$k$ nesting) resample model parameters $\\sigma_1$ and $\\delta_1$.">>=
cesResamplePlotSigma_1Delta_1(energyType="Q", nest="(le)k")
@

<<CESq_sigma_delta_Scatter_Graph_lek, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $q$, ($le$)$k$ nesting) resample model parameters $\\sigma$ and $\\delta$.">>=
cesResamplePlotSigmaDelta(energyType="Q", nest="(le)k")
@

<<CESq_lambda_gamma_Scatter_Graph_ekl, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $q$, ($ek$)$l$ nesting) resample model parameters $\\lambda$ and $\\gamma$.">>=
cesResamplePlotLambdaGamma(energyType="Q", nest="(ek)l")
@

<<CESq_sigma_1_delta_1_Scatter_Graph_ekl, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $q$, ($ek$)$l$ nesting) resample model parameters $\\sigma_1$ and $\\delta_1$.">>=
cesResamplePlotSigma_1Delta_1(energyType="Q", nest="(ek)l")
@

<<CESq_sigma_delta_Scatter_Graph_ekl, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $q$, ($ek$)$l$ nesting) resample model parameters $\\sigma$ and $\\delta$.">>=
cesResamplePlotSigmaDelta(energyType="Q", nest="(ek)l")
@

@@
